Statistical paradoxes in coronavirus case-counts: selection bias, measurement error, and the COVID-19 pandemic

### 2021-02-22 write-up/covid-writeup.tex
Update covid-writeup.tex

\subsection{Related work.}

@@

In this section we provide the necessary background to understand COVID-19 diagnostic and serologic testing, their respective scientific uses in managing the pandemic, and the corresponding data streams.

>>>>

\subsection{Related work}

@@

In this section we provide the necessary background to understand COVID-19 diagnostic and serologic testing, their respective scientific uses in managing the pandemic, and the data streams we consider in this manuscript.
